О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-30 pps-linear-bound/pps-linear-lower-bound.tex
irreducible -> prime

\begin{definition}
	We will call an integral point set $M$ \textit{irreducible}, if the greatest common divisor
	of all the distances occuring in $M$ is 1.
\end{definition}

If an integral point set is irreducible,
then it cannot be squashed to an integral point set of the same power and structure but smaller diameter.

\begin{hypothesis}
	\label{hyp:irreducible_planar}
	For every $m \geq 2$, $n \geq m+1$, $d \geq 1$ there exists an \textbf{irreducible}
	integral point set $M$ of $n$ points in $m$-dimensional Euclidean space
	where $M$ contains points $M_1$ and $M_2$ such that distance between $M_1$ and $M_2$ is exactly $d$.
\end{hypothesis}

For $m \geq 3$, Hypothesis~\ref{hyp:irreducible_planar} can be easily proved:
indeed, we can just take a facher integral point set according to Construction~\ref{con:planar_set_with_minimeter_1}
with sufficiently large height and then apply the ``blowing up'' procedure described in~\cite[Theorem 1.3]{kurz2008bounds},
replacing the out-of-line point with an $(m-2)$-dimensional simplex with proper side length.
That simplex will consist of $m-1$ points;
we can throw out up to all points $M_J$, except the two points with distance 1.
So, the set consists of $m+1$ or more points and has distance 1 occuring in it.
As distance 1 occurs in the obtained set, it is irreducible.

So, Hypothesis~\ref{hyp:irreducible_planar} needs proof only for $m=2$.

>>>>

\begin{definition}
	\cite{noll1989nclusters}
	We will call an integral point set $M$ \textit{prime}, if the greatest common divisor
	of all the distances occuring in $M$ is 1.
\end{definition}

If an integral point set is prime,
then it cannot be squashed to an integral point set of the same power and structure but smaller diameter.

\begin{hypothesis}
	\label{hyp:prime_planar}
	For every $m \geq 2$, $n \geq m+1$, $d \geq 1$ there exists an \textbf{prime}
	integral point set $M$ of $n$ points in $m$-dimensional Euclidean space
	where $M$ contains points $M_1$ and $M_2$ such that distance between $M_1$ and $M_2$ is exactly $d$.
\end{hypothesis}

For $m \geq 3$, Hypothesis~\ref{hyp:prime_planar} can be easily proved:
indeed, we can just take a facher integral point set according to Construction~\ref{con:planar_set_with_minimeter_1}
with sufficiently large height and then apply the ``blowing up'' procedure described in~\cite[Theorem 1.3]{kurz2008bounds},
replacing the out-of-line point with an $(m-2)$-dimensional simplex with proper side length.
That simplex will consist of $m-1$ points;
we can throw out up to all points $M_J$, except the two points with distance 1.
So, the set consists of $m+1$ or more points and has distance 1 occuring in it.
As distance 1 occurs in the obtained set, it is prime.

So, Hypothesis~\ref{hyp:prime_planar} needs proof only for $m=2$.
